
\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'


\usepackage[scale=0.8]{geometry} % Reduce document margins
\usepackage[utf8]{inputenc}

\setlength{\makecvtitlenamewidth}{12cm}
\renewcommand*{\namefont}{\fontsize{24}{29}\mdseries\upshape}
     
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{BHARADHWAJ C.N} % Your first name
\familyname{} % Your last name

% All information in this block is optional, comment out any lines you don't need

\address{10/102, "SHREYAS" \\ Chittur-Palakkad(P.O), Palakkad\\}{Kerala, India - 678101}
\mobile{+91 8891184835}
\email{bharadhwaj10@gmail.com}


%----------------------------------------------------------------------------------------

\begin{document}



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cvlistitem{Pursuing Bachelors degree in \textit{Computer Science and Engineering} from NSS College of Engineering, Palakkad}

\cvlistitem{Completed Higher Secondary Education in \textit{Computer Science} from Vijayamatha C.H.S.S, Chittur, Palakkad}

\cvlistitem{Completed High School Education from Vijayamatha C.H.S.S, Chittur, Palakkad}



\section{Other Courses}

\cvlistitem{Completed \textit{Diploma in Java Technology} from National Institute of Information Technolgy, Palakkad}



\section{Technical skills}

\cvcomputer
{\textbf{Operating System}}{Gnu/Linux, OS X, Windows}
{\textbf{Programming Languages}}{C, C++, Python, Java, Objective C, HTML/CSS, JavaScript}
\cvcomputer
{\textbf{Development Tools}}{Git, SublimeText, Nano, Xcode, Netbeans, Eclipse}
{\textbf{Frameworks}}{Java EE, Bootstrap, Flask, SQLAlchemy}
\cvcomputer
{\textbf{Software Packages}}{MySQL, SQLite, Microsoft SQL Server, \LaTeX, Gimp/Photoshop, Office Suites.}
{\textbf{Cloud Platforms}}{OpenShift, Heroku}
{}{}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


\section{Events Organized and Volunteer Work}

\cventry{November 2014}{Classes for +2 Students}{}{Kendriya Vidyalaya 1, Palakkad}{}{Conducted classes for +2 students of Kendriya Vidyalaya on Computer Science for their curriculum.}


\cventry{September 2014}{Bash 'em Up - Shell Scripting Competition}{Gamaya 2k14}{NSS College of Engineering}{}{Co-hosted a shell scripting competition that had an online prelims and offline finals.}

\cventry{March 2014}{Workshop on Free software and open web}{}{NSS College of Engineering}{}{Helped to organize a two day workshop on FOSS and Mozilla's Open Web campaign}

\cventry{2012}{ABACUS Workshops and Talks}{}{NSS College of Engineering}{}{Helped to organize many Workshops and Talks on behalf of ABACUS, NSSCE.}


\section{Positions}
\cventry{July 2014 -- }{ABACUS}{Executive Member}{NSS College of Engineering}{}{A Bona fide Association for Computer Users and Students (ABACUS) is a student organization of NSSCE for Computer Science and Engineering Students.}{}


\cventry{July 2013 -- }{National Service Scheme}{Volunteer}{NSS College of Engineering}{}{National Service Scheme, Technical Educaton Department volunteer of Unit 128.}{}

\newpage
%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------

\section{Projects and Work Experience}

\cvlistitem
{\textbf{TIM - TIM Isn't Moodle}
  \\College Miniproject. An online space for communication between teachers and students, with email and SMS notifications\\}

\cvlistitem
{\textbf{NSS Hostels Website}
  \\A freelance work for Hostels of NSSCE. A website for college hostels of NSSCE.\\}

\cvlistitem
{\textbf{palacharakkukada.com}
  \\Project done for obtaining Diploma in Java Technology from NIIT. An online e-shopping site.\\}

\cvlistitem
{\textbf{Student Report Card}
  \\Higher secondary school project. A sample report card for students of particular class.\\}



\section{Achievements}
\cventry{September 2014}{Krama jwala}{}{NSS College of Engineering, Palakkad}{}{Won \textbf{first prize} in the National Level Contest based on Embedded Systems/Digital Electronics conducted as a part of Gamaya 2k14, Tech fest} \\ 

\cventry{September 2014}{Coding Competition - TCS Codevita}{}{Tata Consultancy Services}{}{Obtained \textbf{Rank 204} on coding competition, Codevita conducted by TCS, globally over 10 nations.} \\

\cventry{  January 2010}{IT Web Page Designing}{State School IT Fest}{Technopark, Thiruvananthapuram}{}{Participated in the state level IT Web Page Designing for school students, organized by Govt. Of Kerala}


\section{Interests and Hobbies}
\cvlistitem{An active reader on latest technology and websites\\}

\cvlistitem{Interested in coding and web page designing.\\}

\cvlistitem{Love to play outdoor games.\\}

\cvlistitem{Interested in photography and drawing.\\}






\end{document}
