
\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\usepackage{lastpage}


\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'


\usepackage[scale=0.8]{geometry} % Reduce document margins
\usepackage[utf8]{inputenc}

\setlength{\makecvtitlenamewidth}{12cm}
\renewcommand*{\namefont}{\fontsize{24}{29}\mdseries\upshape}

%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{BHARADHWAJ C.N} % Your first name

\familyname{} % Your last name
\rfoot{\addressfont\itshape\textcolor{gray}{\thepage}}

% All information in this block is optional, comment out any lines you don't need
\title{}

\address{10/102, "SHREYAS" \\ Chittur-Palakkad(P.O), Palakkad\\}{Kerala, India - 678101}
\mobile{+91 8891184835}
\email{bharadhwaj10@gmail.com}
\social[linkedin]{https://in.linkedin.com/in/bharadhwajcn}

%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	CAREER OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{Career Objective}

\hspace*{2.5cm} Highly self motivated guy who loves to work in a challenging environment that provides \\
\hspace*{2.5cm} better work culture, generous opportunities for learning and also to achieve organisational \\
\hspace*{2.5cm} goals.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education Qualification}

~\\
\begin{table}
\hspace*{2cm}
\setlength\arrayrulewidth{.4pt}
\setlength\parindent{30pt}
\setlength\tabcolsep{6pt}
\begin{tabular}{|c|l|c|c|c|}
\hline
\textbf{Graduation} & \multicolumn{1}{c|}{ \textbf{Name of University}} & \textbf{State/CBSE} & \textbf{Year} & \textbf{Aggregate} \\ \hline
B.Tech     & \begin{tabular}[c]{@{}l@{}}  NSS College of Engineering,  \\ Palakkad - 8*\end{tabular}      & -          & 2012-2016 & 7.71     \\ \hline
HSE        & \begin{tabular}[c]{@{}l@{}}  Vijayamatha Convent H.S.S,  \\ Chittur, Palakkad.\end{tabular} & State      & 2010-2012 & 91.75     \\ \hline
SSLC       & \begin{tabular}[c]{@{}l@{}}  Vijayamatha Convent H.S.S,  \\ Chittur, Palakkad.\end{tabular} & State      & 2010      & 95        \\ \hline
\end{tabular}
\end{table} 

~\\

\hspace*{2cm} * Completed Bachelors degree in Technology in \textit{Computer Science and Engineering} from \\ 
\hspace*{2.3cm} NSS College of Engineering, Palakkad.
\subsection{Other Courses}
\cvlistitem{Completed \textbf{Diploma in Java Technology} with \textit{Excellent} grade from  NIIT, Palghat. ~\\}

\cvlistitem{Completed \textbf{SV.CO's online entrepreneurship program} under the domain \textit{Fintech} from  Startup Village, Kochi. ~\\}


%----------------------------------------------------------------------------------------
%	INTERNSHIP SECTION
%----------------------------------------------------------------------------------------

\section{Internship}

\cventry{April-July 2015}{Intern at QBurst Technologies}{}{CM Mathew Arcade, Calicut}{}{Worked as Intern at QBurst Technologies, Calicut for 5 weeks and did project on iOS app development.}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\cvlistitem
{\textbf{A Scalable Model for Efficient Information Diffusion in Large Real world Networks.}
  \\Main project in B.Tech curriculum. This model aims in effectively finding a set of Influential Node from a large real world graph which contains Billions of edges which helps in diffusing information in the whole graph. Tools used were \textbf{Apache Hadoop, Apache Giraph, Maven}. \\}

\cvlistitem
{\textbf{iOS Application for accurate distance and angle measurements}
  \\Project done during internship. An iOS app for drawing plan of a building with automatic accurate distance measurement. Tools used are \textbf{Xcode 6.3, Git}. \\}

\cvlistitem
{\textbf{TIM - TIM Isn't Moodle}
  \\Project done as part of Academics. An online space for communication between teachers and students, with email and SMS notifications. Technology stack used is \textbf{Python Flask}, other tools used are \textbf{Sqlite3}. \\}
  
\cvlistitem
{\textbf{palacharakkukada.com}
  \\Project done for obtaining Diploma in Java Technology from NIIT, Palghat. An online e-shopping site which supports mock payments. Technology stack used is \textbf{Java EE}, other tools used are \textbf{Netbeans 6.0.1, Microsoft SQL Server 2008}. \\}


%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Technical skills}

\cvcomputer
{\textbf{Operating System}}{Gnu/Linux, Windows, OS X}
{\textbf{Programming Languages}}{C, C++, Python, Java, Objective C}
~\\
~\\
\cvcomputer
{\textbf{Development Tools}}{Git, SublimeText, Nano, Netbeans, XCode}
{\textbf{Frameworks}}{Bootstrap, Flask, Java EE, SQLAlchemy}
~\\
~\\
\cvcomputer
{\textbf{Software Packages}}{MySQL, SQLite, Microsoft SQL Server, \LaTeX, Gimp/Photoshop, Office Suites.}
{\textbf{Cloud Platforms}}{OpenShift, Heroku}
{}{}



%----------------------------------------------------------------------------------------
%	AREA OF INTEREST SECTION
%----------------------------------------------------------------------------------------

\section{Area of Interest}

\cvlistitem{Web page designing.}

\cvlistitem{Programming.}

\cvlistitem{Open source contribution.}



%----------------------------------------------------------------------------------------
%	EVENTS ORGANIZED SECTION
%----------------------------------------------------------------------------------------


\section{Events Organized and Volunteer Work}

\cventry{February 2016}{Dvaita'16}{Technical Fest}{NSS College of Engineering}{}{Organised the national level technical fest DVAITA'16. Was assigned the duty of Sponsorship head and official panel member for the fest.}

\cventry{September 2014}{Bash 'em Up - Shell Scripting Competition}{Gamaya 2k14}{NSS College of Engineering}{}{Co-hosted a shell scripting competition that had an online prelims and offline finals.}

\cventry{March \hspace*{1cm}2014}{Workshop on Free software and open web}{}{NSS College of Engineering}{}{Helped to organize a two day workshop on FOSS and Mozilla's Open Web campaign}

\cventry{June 2013 - May 2015}{National Service Scheme}{}{NSS College of Engineering}{}{Worked for National Service Scheme under Technical cell Kerala and organised many social beneficiary volunteer works.}

\cventry{2012}{ABACUS Workshops and Talks}{}{NSS College of Engineering}{}{Helped to organize many Workshops and Talks on behalf of ABACUS, NSSCE.}

\cventry{June 2005 - May 2010}{Bharath Scouts and Guides}{}{36th B.P Open Troop}{}{Rajyapuraskar scout.}


%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}
\cventry{September 2014}{Krama jwala}{}{NSS College of Engineering, Palakkad}{}{Won \textbf{first prize} in the National Level Contest based on Embedded Systems/Digital Electronics conducted as a part of Gamaya 2k14, Tech fest\\}

\cventry{September 2014}{Coding Competition - TCS Codevita}{}{Tata Consultancy Services}{}{Obtained \textbf{Rank 204} on coding competition, Codevita conducted by TCS, globally over 10 nations.\\}

\cventry{January 2010}{IT Web Page Designing}{State School IT Fest}{Technopark, Thiruvananthapuram}{}{Participated in the state level IT Web Page Designing for school students, organized by Govt. Of Kerala}

\end{document}
